### 2021-04-21 input/abstract.tex
meow

  %%% Our proposal
  \noindent In this paper, we abstract content indexing as distributed
  partitioning: every \process only indexes its closest replica, and
  connected \processes with similar index compose a partition. Our
  decentralized implementation \NAME
  \begin{inparaenum}[(i)]
  \item is efficient, for it uses partitions to lock down the traffic
    generated by its operations to relevant \processes, yet it
  \item guarantees that every \process eventually acknowledges its
    partition despite concurrent operations.
  \end{inparaenum}
  %% When a \node replicates a content, it notifies all \nodes (new
  %% members of its partition) that are closer from it than any other
  %% replica; When a \node destroys a replica, it notifies members of
  %% its partition to switch to another closer partition. \NAME
  %% guarantees that eventually, every \process knows its best
  %% partition, hence its closest replica, despite concurrent
  %% operations and receipt orders.
  Our complexity analysis supported by simulations shows that \NAME
  scales well in terms of generated traffic and termination time,
  especially in dynamic Edge infrastructures. As such, \NAME could
  constitute the building block of new geo-distributed services.
\end{abstract}

>>>>

  %%% Our proposal
  \noindent In this paper, we abstract content indexing as distributed
  partitioning:
\TODO{weird}
  every \process only indexes its closest replica, and
  connected \processes with similar index compose a partition. Our
  decentralized implementation \NAME
  \begin{inparaenum}[(i)]
  \item is efficient, for it uses partitions to lock down the traffic
    generated by its operations to relevant \processes, yet it
  \item guarantees that every \process eventually acknowledges its
    partition despite concurrent operations.
  \end{inparaenum}
  %% When a \node replicates a content, it notifies all \nodes (new
  %% members of its partition) that are closer from it than any other
  %% replica; When a \node destroys a replica, it notifies members of
  %% its partition to switch to another closer partition. \NAME
  %% guarantees that eventually, every \process knows its best
  %% partition, hence its closest replica, despite concurrent
  %% operations and receipt orders.
  Our complexity analysis supported by simulations shows that \NAME
  scales well in terms of generated traffic and termination time,
  especially in dynamic \TODO{weird, we do not really test dynamic}
Edge infrastructures. As such, \NAME can
  constitute the building block of new geo-distributed services.
\end{abstract}

### 2021-04-21 input/figpartitionintuition.tex

\begin{figure*}
\centering
\subfloat[Initial configuration - Every nodes get the content from node $R$\label{fig:partition_intuitionA}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-1.png}}\hfill
\subfloat[Adding a second replica in node $G$ partitions the network nodes in $2$ sets.\label{fig:partition_intuitionB}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-2.png}}\hfill
\subfloat[A third replica is created in node $B$ resulting in $3$ partitions.\label{fig:partition_intuitionC}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-3.png}}\hfill
\subfloat[Removing the green partition: only $2$ partitions remain.\label{fig:partition_intuitionD}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-4.png}}
%
\caption{Example of the french RENATER topology (edges are not drawn):
  Partitions shrink or expand according to the creation or removal of
  replicas. Ideally, only a subset of nodes should be informed of
  these events, according to their place in the
  topology.} \label{fig:partition_intuition}
\end{figure*}

>>>>

\begin{figure*}
\centering
\subfloat[\Process~$R$ efficiently advertises its content using epidemic propagation. Every \process requests $R$ if needed.\label{fig:partition_intuitionA}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-1.png}}
\hfill
\subfloat[\Process $G$ creates a second replica splitting the red set in two. \Processes request their closest replica host.\label{fig:partition_intuitionB}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-2.png}}\hfill
\subfloat[\Process $B$ creates another replica. \Process~$B$ needs to notify only a small subset of \processes.\label{fig:partition_intuitionC}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-3.png}}\hfill
\subfloat[\Process $G$ destroys its replica. \Processes that belong to its partition must find the closest partition they are in.\label{fig:partition_intuitionD}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-4.png}}
%
\caption{The french RENATER topology. Partitions
  grow and shrink depending on creations and removals of
  replicas.} \label{fig:partition_intuition}
\end{figure*}
